\documentclass[sigconf]{acmart}
\usepackage{subfig}
\usepackage{tabulary}
\usepackage{threeparttable}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{relsize,xspace}
\usepackage[framemethod=tikz,
innerleftmargin=1pt,
innerrightmargin=1pt,
innertopmargin=1pt,
innerbottommargin=1pt,
skipabove=6pt,
skipbelow=6pt,
splittopskip=2pt,
splitbottomskip=2pt,
roundcorner = 0pt
]{mdframed}
\usepackage{listings}
\usepackage{multirow}
\usepackage{microtype}

\definecolor{light-gray-fork}{gray}{0.925}
\definecolor{light-gray-mainline}{gray}{0.8}
\definecolor{javared}{rgb}{0.6,0,0} % for strings
\definecolor{javagreen}{rgb}{0.25,0.5,0.35} % comments
\definecolor{javapurple}{rgb}{0.5,0,0.35} % keywords
\definecolor{javadocblue}{rgb}{0.25,0.35,0.75} % javadoc
\lstdefinestyle{all}{
	basicstyle=\fontsize{11}{11}\selectfont\ttfamily\footnotesize,
	numbers=none,
	xleftmargin=0.1cm,
	xrightmargin=0.1cm,
	stepnumber=1,
	showstringspaces=false,
	tabsize=1,
	breaklines=true,
	breakatwhitespace=false,
	frame=single,
	commentstyle=\color{gray}
}

\lstdefinestyle{result} {
	frame=none,
	escapechar=`,
	language=Java,
	basicstyle=\fontsize{11}{12}\scriptsize,
	postbreak=\mbox{\textcolor{gray}{$\hookrightarrow$}\space},
	keywordstyle=\color{javapurple}\bfseries,
	stringstyle=\color{javared},
	commentstyle=\color{javagreen},
	morecomment=[s][\color{javadocblue}]{/**}{*/},
	moredelim=**[is][\color{red}]{@@}{@@},
}

\lstdefinestyle{dataset} {
	frame=single,
	escapechar=`,
	language=Java,
	basicstyle=\fontsize{11}{12}\scriptsize,
	postbreak=\mbox{\textcolor{gray}{$\hookrightarrow$}\space},
	keywordstyle=\color{javapurple}\bfseries,
	stringstyle=\color{javared},
	commentstyle=\color{javagreen},
	morecomment=[s][\color{javadocblue}]{/**}{*/},
	moredelim=**[is][\color{red}]{@@}{@@},
}
\usepackage{array}
\newcommand*\rotbf[1]{\rotatebox{90}{\textbf{#1}}}
\newcommand{\specialcell}[2][c]{\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\newcommand{\specialcellbold}[2][c]{%
	\bfseries
	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}%
}
\newcommand\parhead[1]{\vspace{.26mm}\noindent\textbf{{#1}}.}  
\newcommand{\secref}[1]{Section~\ref{#1}}
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\Figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\lstref}[1]{Listing~\ref{#1}}

\newcommand{\mtnote}[1]{\textsuperscript{\TPTtagStyle{#1}}}
\newcommand\theader[1]{\textsf{{#1}}}
\newcommand\featureName[1]{\textit{\textsf{{#1}}}}
\newcommand\mformula[1]{$\mathnormal{{#1}}$}

\newcommand{\tb}[1]{{\textsf{TB}[\smaller\sffamily\color{blue} #1}]}
\newcommand{\rh}[1]{{\textsf{RH}[\smaller\sffamily\color{orange} #1}]}
\newcommand{\mm}[1]{{\textsf{MM}[\smaller\sffamily\color{green!10!orange!90!} #1}]}
\newcommand{\wm}[1]{{\textsf{WM}[\smaller\sffamily\color{red} #1}]}
\newcommand{\es}{ElasticSearch\xspace}

\usepackage{xcolor}

\newcommand{\quotebox}[3]{\vspace{.5em}\noindent\begin{tikzpicture}
\node[align=center,draw,thin,minimum width=\columnwidth,inner sep=2.2mm] (titlebox)%
{\parbox{0.95\columnwidth}{\noindent\textit{#2}}};\node[fill=white] (W) at ([xshift=#3]titlebox.south) {\small #1};%
\end{tikzpicture}}

\newcounter{recommendationno}
\newcommand{\recommendation}[1]{\refstepcounter{recommendationno}Recommendation \the\numexpr\value{recommendationno}~(\factor{#1})}
\newcounter{observationno}
\newcommand{\observation}[1]{\refstepcounter{observationno}Observation \the\numexpr\value{observationno}~(#1)}


\setcopyright{acmcopyright}
\copyrightyear{2020}
\acmYear{2020}
\acmDOI{}

\setcopyright{none}

\begin{document}
\title{Feature-Oriented Defect Prediction}
\renewcommand{\shorttitle}{}

\author{Stefan Strüder}
\affiliation{University of Koblenz-Landau, Germany}

\author{Daniel Strüber}
\affiliation{Radboud University Nijmegen, Netherlands}

\author{Mukelabai Mukelabai}
\affiliation{Chalmers $|$ University of Gothenburg, Sweden}

\author{Thorsten Berger}
\affiliation{Chalmers $|$ University of Gothenburg, Sweden}

\renewcommand{\shortauthors}{}


\begin{abstract}
Software errors are a major nuisance in software development and can lead not only to damage to reputation but also to considerable financial losses for companies. For this reason, numerous techniques for detecting and predicting defects have been developed over the past decade, which are largely based on machine learning methods. These techniques are usually aimed at predicting defects at the file level. However, in recent years the popularity of feature-based software development has been increasing: a paradigm that relies on functional increments of a software system (features) and thus ensures a wide variability of the software product. A common implementation technique for features is based on annotations with preprocessor instructions, such as \texttt{\#IFDEF} and \texttt{\#IFNDEF}, whose code is spread over several files of the software source code ("code scattering"). A bug in such feature code can have far-reaching consequences for the functionality of the entire software. If a part of the feature code contains defects, the entire function of the feature becomes faulty and may lead to the failure of the entire functionality of the software (features are "cross-cutting"). This problem is the subject of this thesis. A prediction technique for defective features is developed, which is based on machine learning methods. The evaluation of eight classifiers, each based on an individual classification algorithm, shows that the feature-based dataset created for this thesis allows an accuracy of up to $84\%$ for the prediction of defective or defect-free features. It is also shown how the feature oriented aspect was integrated into the creation of the dataset and what results were achieved compared to the traditional file-based methodology. This comparison showed that the additional inclusion of the feature aspect in the file-based defect prediction does not have a significant impact on the prediction results.

\end{abstract}

\keywords{}

\maketitle

\input{introduction}

\input{background}

\input{methodology}

\input{evaluation}

\input{discussion}

\input{conclusion}


%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{doc}

%%
%% If your work has an appendix, this is the place to put it.
%\appendix


\end{document}
\endinput
